Parameter Recovery Validation

### 2025-06-15 nbs/concepts/parameter-recovery-validation/index.qmd
docs(parameter-recovery-validation): fix spacing
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

**Practical example:**
- **Experimental setup**: 24-hour differentiation time course
- **Posterior estimate**: $T_M \approx 3.0$
- **Inferred characteristic timescale**: $24/3 = 8$ hours
- **Biological interpretation**: Cellular processes (splicing, degradation) occur on ~8 hour timescales

@@

**Example interpretations:**
- $t^*_{on,i} = 1.5$, $T_M = 5.0$: Gene activates 30% through the process
- $t^*_{on,i} = -0.5$: Gene was already active 0.5 timescales before observation began

>>>>

**Practical example:**

- **Experimental setup**: 24-hour differentiation time course
- **Posterior estimate**: $T_M \approx 3.0$
- **Inferred characteristic timescale**: $24/3 = 8$ hours
- **Biological interpretation**: Cellular processes (splicing, degradation) occur on ~8 hour timescales

@@

**Example interpretations:**

- $t^*_{on,i} = 1.5$, $T_M = 5.0$: Gene activates 30% through the process
- $t^*_{on,i} = -0.5$: Gene was already active 0.5 timescales before observation began
